R for Clinical Study Reports and Submission

### 2021-09-15 tlf-overview.Rmd
update tlf-overview

- provide simple "verb" functions that correspond to each component of a table, 
  to help you translate data frame to a table in RTF file.
- enable pipes (`%>%`). 
- only focus on **table format**. 
  Data manipulation and analysis shall be handled by other R packages. (e.g. `tidyverse`)

@@

To explore the basic RTF generation verbs in `r2rtf`, 
we'll use the dataset `r2rtf_adae` saved in the `r2rtf` package. 
This dataset contain adverse events (AE) information from a clinical trial.

@@

`r2rtf` aims to provide one function for each type of table layout.
Commonly used verbs includes:

@@

All these verbs are designed to enable the usage of pipes (`%>%`).
A full list of all functions can be found in [package reference](https://merck.github.io/r2rtf/reference/index.html)

@@

If we want to adjust the width of each column to 
provide more space to the first column, 
this can be achieved by updating `col_rel_width` argument in `rtf_body`.

@@

If we want to remove the top border of `"Adverse Events"` in the header, 
we can change default value `"single"` to `""` in `border_top` argument as showed below.

`r2rtf` support 26 different border types. The details can be found in 
the [r2rtf package website](https://merck.github.io/r2rtf/articles/rtf-row.html#border-type).

@@

Those features will be introduced when we first use them in the rest of chapters.

There are other R packages that can create TLFs in `.rtf` or `.docx` format.
Interested reader can refer "Microsoft/LibreOffice Formats" section in 
[CRAN Task View: Reproducible Research](https://cran.r-project.org/web/views/ReproducibleResearch.html)
for an overview.

>>>>

- provide simple "verb" functions that correspond to each component of a table, 
  to help you translate a data frame to a table in RTF file.
- enable pipes (`%>%`). 
- only focus on the **table format**. 
  Data manipulation and analysis shall be handled by other R packages. (e.g. `tidyverse`)

@@

To explore the basic RTF generation verbs in `r2rtf`, 
we'll use the dataset `r2rtf_adae` saved in the `r2rtf` package. 
This dataset contains adverse events (AE) information from a clinical trial.

@@

`r2rtf` aims to provide one function for each type of table layout.
Commonly used verbs include:

@@

All these verbs are designed to enable the usage of pipes (`%>%`).
A full list of all functions can be found in the 
[r2rtf package reference](https://merck.github.io/r2rtf/reference/index.html)

@@

If we want to adjust the width of each column to 
provide more space to the first column, 
this can be achieved by updating the `col_rel_width` argument 
in the `rtf_body` function.

@@

If we want to remove the top border of `"Adverse Events"` in the header, 
we can change the default value `"single"` to `""` in the `border_top` argument as showed below.

`r2rtf` support 26 different border types. The details can be found on 
the [r2rtf package website](https://merck.github.io/r2rtf/articles/rtf-row.html#border-type).

@@

Those features will be introduced when we first use them in the rest of the chapters.

There are other R packages that can create TLFs in `.rtf` or `.docx` format.
Interested readers can refer "Microsoft/LibreOffice Formats" section in 
[CRAN Task View: Reproducible Research](https://cran.r-project.org/web/views/ReproducibleResearch.html)
for an overview.
